Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-03 latex/main.tex
WIP

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{tabular}{lrrrrl}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & averted & left & right & samples & nested \\
\midrule
XC & 37 & 26768 & 27390 & 5 & \{\} \\
XBR & 22 & 22034 & 22190 & 1 & \{\} \\
XA & 16 & 20411 & 21765 & 39 & \{\} \\
XS & 11 & 9054 & 10449 & 17 & \{\} \\
XL & 8 & 5925 & 8393 & 64 & \{\} \\
XBG & 8 & 22305 & 22917 & 25 & \{\} \\
XBD & 7 & 23020 & 24620 & 30 & \{\} \\
XQ & 7 & 4322 & 5386 & 55 & \{BA.2:37, $\star$\} \\
XBB & 6 & 22332 & 22577 & 6452 & \{BA.2:1\} \\
XM & 6 & 17411 & 21595 & 26 & \{BA.2:16, XAL:3\} \\
XBF & 5 & 5184 & 9866 & 185 & \{\} \\
XF & 5 & 5387 & 6402 & 16 & \{\} \\
XY & 5 & 11538 & 12880 & 23 & \{\} \\
XG & 4 & 5925 & 6513 & 3 & \{\} \\
XW & 4 & 2833 & 4321 & 32 & \{\} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & averted & left & right & total & by pango \\
\midrule
XAE+ & 6 & 24504 & 26060 & 253 & {BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & 1156 & {XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & 12 & {XBM:10, BF.3:2} \\
XAF & 5 & 10199 & 10447 & 36 & {BA.2:35, XAF:1} \\
XJ & 5 & 13196 & 17410 & 85 & {XJ:68, BA.2:17} \\
\bottomrule

\end{tabular}

>>>>

% This table is generated by the notebook tab_pango_x_events
\begin{table}
\caption{ARG events associated with Pango X lineages.
Each row corresponds to the oldest node assigned the specified
Pango lineage and the ancestor of all nodes assigned that label
(except XBB, XBB.1 and XM; see STAR methods). [MORE DETAILS]
\label{tab:pango_x_lineages}}
\begin{tabular}{lrrrrll}
\toprule
\multicolumn{5}{l}{Type I RE event: monophyletic for pango}\\
pango & averted & left & right & samples & nested \\
\midrule
XC & 37 & 26768 & 27390 & 5 & \{\} \\
XBR & 22 & 22034 & 22190 & 1 & \{\} \\
XA & 16 & 20411 & 21765 & 39 & \{\} \\
XS & 11 & 9054 & 10449 & 17 & \{\} \\
XL & 8 & 5925 & 8393 & 64 & \{\} \\
XBG & 8 & 22305 & 22917 & 25 & \{\} \\
XBD & 7 & 23020 & 24620 & 30 & \{\} \\
XQ & 7 & 4322 & 5386 & 55 & \{BA.2:37, $\star$\} \\
XBB & 6 & 22332 & 22577 & 6452 & \{BA.2:1\} \\
XM & 6 & 17411 & 21595 & 26 & \{BA.2:16, XAL:3\} \\
XBF & 5 & 5184 & 9866 & 185 & \{\} \\
XF & 5 & 5387 & 6402 & 16 & \{\} \\
XY & 5 & 11538 & 12880 & 23 & \{\} \\
XG & 4 & 5925 & 6513 & 3 & \{\} \\
XW & 4 & 2833 & 4321 & 32 & \{\} \\
\midrule
\multicolumn{5}{l}{Type II RE event}\\
alias & averted & left & right & total & by pango \\
\midrule
XAE+ & 6 & 24504 & 26060 & 253 & {BA.2:156, XZ:48, XAP:20, XAC:18, XAE:9, XAD:2} \\
XE/XH & 6 & 10448 & 11283 & 1156 & {XE:1116, BA.2:37, XH:2, XAF:1} \\
XBH & 6 & 15452 & 22001 & 6 & {BA.2:4, XBH:2} \\
XBM & 6 & 22305 & 22917 & 12 & {XBM:10, BF.3:2} \\
XAF & 5 & 10199 & 10447 & 36 & {BA.2:35, XAF:1} \\
XJ & 5 & 13196 & 17410 & 85 & {XJ:68, BA.2:17} \\
\midrule
\multicolumn{5}{l}{Nested monophyletic Pango X lineage}\\
pango & alias & path len & time & mutations & samples & nested \\
\midrule
XAP & XAE+ & 4 & 67 & 1 & 20 & \{\} \\
XZ & XAE+ & 4 & 48 & 1 & 48 & \{\} \\
XAE & XAE+ & 2 & 47 & 7 & 9 & \{\} \\
XAF & XAF & 5 & 140 & 8 & 1 & \{\} \\
XAL & XM & 3 & 66 & 2 & 3 & \{\} \\
XR & XQ & 3 & 11 & 4 & 17 & \{BA.2:1\} \\
XU & XQ & 6 & 103 & 4 & 1 & \{\} \\
XAM & XQ & 6 & 43 & 3 & 21 & \{\} \\
XAA & XQ & 6 & 33 & 3 & 17 & \{\} \\
XAG & XQ & 6 & 55 & 4 & 6 & \{\} \\

\bottomrule
\end{tabular}
